Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-05 prop_letter.tex
prop_letter.tex \section{Introduction} Update comments...

The paper is organized as follows.   In Sec.\ \ref{sec:fuzzy} we begin by introducing the foundations of quantum probability space and fuzzy measurement.  We then move on to introduce the concept of quantum interval valued probability in Sec.\ \ref{sec:Interval-Uncertainty}.  This QIVPM will provide the mathematical framework to quantify the impact of finite precision measurements on quantum mechanics.  For instance, in Sec.\ \ref{sec:Kochen-Specker},  we quantify the domain of validity of a  contextual measurement, thus addressing the conditions under which the Kochen-Specker theorem applies.  This provides a way of resolving the Meyer-Mermin debate\nb\footnote{Cabello has referred to this as the second contextuality war~\citep{Cabello2017}.}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.  In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid in a universe with bounded resources, holds asymptotically in a mathematically precise way.  Finally, we present our conclusions in Sec.~\ref{sec:Conclusion}.

>>>>

The paper is organized as follows.   In Sec.\ \ref{sec:fuzzy} we begin by introducing the foundations of quantum probability space and fuzzy measurement.  We then move on to introduce the concept of quantum interval valued probability in Sec.\ \ref{sec:Interval-Uncertainty}.  This QIVPM will provide the mathematical framework to quantify the impact of finite precision measurements on quantum mechanics.  For instance, in Sec.\ \ref{sec:Kochen-Specker},  we quantify the domain of validity of a  contextual measurement, thus addressing the conditions under which the Kochen-Specker theorem applies.  This provides a way of resolving the Meyer-Mermin debate\nb\footnote{There is nothing found when google ``Meyer-Mermin debate.''\\
Cabello has referred to this as the second contextuality war~\citep{Cabello2017}.\\
Jochen Szangolies called this ``the Finite-Precision Problem''~\citep{Szangolies2015}.}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.  In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid in a universe with bounded resources, holds asymptotically in a mathematically precise way.  Finally, we present our conclusions in Sec.~\ref{sec:Conclusion}.
